---
title: "graphTweets"
subtitle: "More Examples"
author: "John Little"
date: '`r Sys.Date()`'
output: html_notebook
---

# Preface

Using the graphTweets package with the rtweet package to generate a network graph.  graphTweet can write a file in "gephi format" -- for which Gephi can open and display

http://john-coene.com/packages/graphTweets/examples

```{r, message=FALSE, warning=FALSE}
library(graphTweets)
library(tidyverse)
library(rtweet)
library(igraph)
library(networkD3)
library(RColorBrewer)
library(ggmap)
library(leaflet)
```

## Get Tweets
```{r getTweets, message=FALSE, warning=FALSE}
dukmbb <- search_tweets("dukembb", n=100, lang = "en")
dukmbb_nRT <- dukmbb%>% 
  filter(is_retweet == FALSE)
```


## Identify Edges
```{r}
edges <- getEdges(data = dukmbb_nRT, tweets = "text", source = "screen_name")

edges <- edges[!duplicated(edges),]

g <- igraph::graph.data.frame(edges, directed = TRUE)

igraph::plot.igraph(g, layout = layout.fruchterman.reingold(g))

```

```{r}
edges <- getEdges(data = dukmbb, tweets = "text", source = "screen_name")
edges <- edges[!duplicated(edges),]

networkD3::simpleNetwork(edges, Source = "source", Target = "target")
```

## Example 2

```{r}

# edges <- getEdges(data = dukmbb, tweets = "text", source = "screen_name")
edges_ex2 <- getEdges(dukmbb_nRT, source = "screen_name", tweets = "text", 
                  str.length = NULL, "favorite_count")
# edges_ex2 <- edges_ex2[!duplicated(edges),]

nodes <- getNodes(edges_ex2, source = "source", target = "target", "favorite_count")

# replace NA with 0
nodes$retweetCount[is.na(nodes$favorite_count)] <- 0

# build graph
g <- igraph::graph.data.frame(edges_ex2, directed = TRUE, vertices = nodes)

```


## make plot for example 2
from http://john-coene.com/packages/graphTweets/examples#example_02

```{r}
pal <- RColorBrewer:::brewer.pal(5, "Dark2")
V(g)$color <- colorRampPalette(pal)(length(V(g)$favorite_count))

# plot vertex size ~ degree
plot(g, layout = layout.fruchterman.reingold(g), vertex.color = V(g)$color,
     vertex.size = log1p(degree(g)) * 3)
```


## Use ggmap to geocode

Although rtweet has `lookup_coords()` I did not find it to be successful for my test.  It may work fine with further review.
```{r }
dukmbb_location <- dukmbb_nRT %>% 
  users_data()

dukmb_coords <- dukmbb_location %>% 
  filter(!is.na(location)) %>% 
  mutate_geocode(location, source = "dsk") %>% 
  select(user_id, name, screen_name, location, lon, lat)
```

## geocode 
```{r}
dukmb_coords %>% 
  filter(!is.na(lon)) %>% 
  leaflet() %>% 
  addTiles() %>% 
  setView(-98.556102, 39.810390, zoom = 4) %>% 
  addMarkers(popup = dukmb_coords$screen_name)
```

