---
title: "rvest demo"
author: "John Little"
date: "`r Sys.Date()`"
output: 
  html_notebook:
    toc: yes
    toc_float: yes
---

## Load packages
```{r, message=FALSE, warning=FALSE}
library(rvest)
library(tidyverse)
```


## Demonstration

Use rvest to scrape tripadvisor.com

Inspired by

- http://notesofdabbler.github.io/201408_hotelReview/scrapeTripAdvisor.html
- `demo(tripadvisor, package = "rvest")`

---

## Star Wars

Goal:  Scrape the first table on the [Carrie Fisher Wikipedia page](https://en.wikipedia.org/wiki/Carrie_Fisher)

```{r}
CarrieFisherWiki <- "https://en.wikipedia.org/wiki/Carrie_Fisher"

CarrieFisherWiki %>% 
  read_html() %>% 
  html_node(".wikitable") %>% 
  html_table()

```

## The Durham Hotel

### html_nodes

Read the HTML for [_The Durham Hotel_ review on TripAdvisor](https://www.tripadvisor.com/Hotel_Review-g49092-d8470160-Reviews-The_Durham_Hotel-Durham_North_Carolina.html)
```{r}
url <- "https://www.tripadvisor.com/Hotel_Review-g49092-d8470160-Reviews-The_Durham_Hotel-Durham_North_Carolina.html"

reviews <- url %>%
  read_html() %>%
  html_nodes("#REVIEWS .innerBubble")
```

---

### html_attr
```{r}
id <- reviews %>%
  html_node(".quote a") %>%
  html_attr("id")
```

---

### html_text
```{r}
quote <- reviews %>%
  html_node(".quote span") %>%
  html_text()

review <- reviews %>%
  html_node(".entry .partial_entry") %>%
  html_text()
```

---

### Variations 

Post processing
```{r}
rating <- reviews %>%
  html_node(".rating .ui_bubble_rating") %>%
  html_attrs() %>% 
  gsub("ui_bubble_rating bubble_", "", .) %>%
  as.integer() / 10

date <- reviews %>%
  html_node(".rating .ratingDate") %>%
  html_attr("title") %>%
  strptime("%b %d, %Y") %>%
  as.POSIXct()
```

---

## Manipulate Data

Preliminary Analysis in a Tibble (modern Data Frame)

### DataFrame (Tibble)
```{r}
dhotel <- data_frame(id, quote, rating, date, review)

dhotel
```

---

### Summary Statistics
```{r}
summary(dhotel$rating)
```

---

### Frequency
```{r}
dhotel %>% 
  group_by(rating) %>% 
  summarise(count = n())
```

---

### Append Variables

Gather location and screen-name information. Select only reviews with a location value
```{r}
memInfo <- url %>%
  read_html() %>% 
  html_nodes("#REVIEWS .col1of2")

loc1 <- memInfo %>% 
  html_node(".location") %>%
  html_text()

screenName <- memInfo %>%
  html_node(".scrname") %>% 
  html_text()

dhotel$scrName <- screenName
dhotel$location <- dhotel_memInfo$loc1

dhotel %>% 
  select(scrName, location, rating, quote) %>% 
  filter(!is.na(location))
```



